An interdisciplinary examination of stress and injury occurrence in athletes

### 2020-06-27 full_paper_v2.Rmd
before intro+methods edits

```{r include=FALSE}
options(scipen=999, digits = 2)
knitr::opts_chunk$set(echo = FALSE)
source("r-files/functions.R")
source("r-files/methods_code.R")
source("r-files/results_code.R")
```

# Introduction {-}

@@

# Methods {-}

@@

## Participants

@@

BNs have recently been used in the sport psychology literature [@Olmedilla2018; @Fuster-Parra2017] and offer several benefits over traditional statistical analysis. 
For example, predictions can be made about any variable in the network, rather than there being a distinction between dependent and independent variables in the data, such as in linear regression models that are often used within the sport psychology literature [@Olmedilla2018; @Bittencourt2016].
Furthermore, the structure of a network can be obtained from both empirical data _and_ prior knowledge about the area of study; the latter being particularly useful when there are a large number of variables in the network, or only a small number of observations are available in the data [@Xiao-xuan2007].
In such instances, a purely data driven approach to learning the network would be time-consuming due to the large parameter space, and inefficient at identifying an approximation of the true network structure. 
Prior knowledge about dependencies between variables can therefore be included in the network structure, while still allowing a data driven approach for unknown dependencies, to improve the overall computation of the network structure [@Heckerman1995; @Xu2015].
The following sections detail the steps taken in the current study to firstly prepare the data for the network, and then obtain the structure of the network that was used for inference.

### Data Preparation

@@

A median split technique was used to discretise the data used in the network into "Low" and "High" levels.
All variables apart from negative and total life events were approximately normally distributed (based on visual inspection, see supplementary table ...) and required no further transformation prior to the median split. 
For the LESCA questionnaire data, a cumulative total of the current, and previous time points was calculated at each time point to account for the potential continuing effect of the life events experienced by athletes over time.
Given the limited support for a relationship between positive life events and injury [@Williams2007], only negative and total life events were included in the network.
Cumulative negative, and cumulative total life event scores at each time point were first log scaled so distributions were approximately normal, and then binarised using the median at each time point (nlelg and tlelg respectively).
In addition to the log scaled cumulative values, an untransformed NLE score from the first time point was included as an additional variable based on previous literature that indicates this variable should have a strong relationship with injury outcome [@Ivarsson2017].

### Network structure

@@

```{r table2, results='asis'}
exampledata <- tibble(
  Participant = c("1", "1", "2", "3", "3"),
  "X_1" = c("T1", "T2", "T1", "T1", "T2"),
  " " = "->",
  "X_2" = c("T2", "T3", "T2", "T2", "T3")
)

kable(
  exampledata,
  caption = "Example of the data arrangement used for the network.",
  escape = TRUE
) %>%
  kable_styling(latex_options = "HOLD_position") %>%
  row_spec(0, bold = TRUE)
```

### Preliminary network structures

@@

Preliminary network structures also revealed strong dependencies between the same variables at subsequent time points. 
For example, the probability that stiffness_1 and stiffness_2 were both "High", or both "Low" was approximately 80%. 
Including the arcs between the same variables from X_1 $\rightarrow$ X_2 did not provide any theoretically meaningful information to the network structure as the majority of participants would be either be in a "Low" or "High" state for each pair of variables in the network. 
To more appropriately assess changes _within_ variables over time, a second BN was investigated by modelling the differences between variables at different time points.
The use of differential equations to model changes in variables over time is a common procedure in BN analysis when there are repeated measurements in the data [@Scutari2017].
To obtain the structure, continuous variables suffixed with _1 were subtracted from variables suffixed with _2 to calculate the difference between variables measured at time points T1 $\rightarrow$ T2 and T2 $\rightarrow$ T3. 
Independent variables were then standardized to allow relative changes between variables to be compared. 
The "injured" variable was also modified to represent whether a participant had sustained an injury at any point over the duration of the study or were healthy for the duration of the study.
The result was a network that explicitly modelled the _amount_ of change within variables between time points, as opposed to the first network that would only have captured changes when the median threshold was crossed from "Low" to "High". 
Identical blacklists to the first network were used for arcs between independent and explanatory variables. 
The nlebase variable was also dropped from the list of explanatory variables to allow the _changes_ in negative life events to be the only life event variable in the network.

To obtain the final networks, the appropriate blacklist and whitelists were provided and a Tabu search algorithm identified the remaining structure of the network. 
The final network structure was obtained by averaging 1000 bootstrapped models [@Efron1993] to reduce the impact of locally optimal, but globally suboptimal network learning, and to obtain a more robust model [@Olmedilla2018].
Arcs that were present in at least 30% of the models were included in the averaged model.
The strength of each arc was determined by the percentage of models that the arc was included in, independent of the arc's direction.
An arc strength of 1 indicates that the arc is always present in the network, with the value decreasing as arcs are found in fewer networks. 
In the respective study arcs above 0.5 were considered "significant" with arcs below 0.5 and above 0.3 "non-significant" [@Scutari2013]. 
Arcs below 0.3 were not included in the model.
The full table of arc strengths for the first and second network are available in S2 Table and S3 Table respectively.

### Network Inference

@@

The second network contained both continuous and discrete data. 
To examine dependencies between continuous variables with arc strengths above 0.5 in the second network, random samples were generated based on the conditional distribution of the nodes included as evidence in the query.
The samples were then extracted and examined with Bayesian linear regression models using the _brms_ package [@Burkner2017a] to determine the relationship between nodes in the network. 
Similar to the first network, the Markov blanket of the "injured" node was also investigated by determining the highest probability of injury with combinations of variables in the Markov blanket below the mean change, at the mean change and above the mean change.

# Results {-}

@@

### First network structure

@@

The conditional probabilities based on all the variables in injured_2 Markov blanket are presented in Table \ref{tab:table9}.
Again, only the three lowest and highest probabilities are shown (complete results in S5 Table).
The combination "Low" FFFS_1, "High" stiffness_2, "High" balance resulted in the greatest  probability of injured_2 being "injured", with the highest probability of injury being `r max(query4$prob)`.
With all other variables held in the "High" state, the probability of injured_2 being "injured" rose from 0.14 to 0.34 when FFFS_1 was in the "Low" compared to "High" state.
The combination of "Low" stiffness, "Low" balance and "High" FFFS resulted in the lowest probability of injured_2 being "injured".

```{r table9, results="asis" }

query4 %>%
  select(7,2:6) %>%
  rename(Probability = "prob") %>%
  `colnames<-`(str_replace_all(colnames(.), "_", "\\\\_")) %>%
  mutate_all(~str_replace_all(., "_", "\\\\_"))%>%
  kable(
    .,
    caption = "Highest and lowest probability of injured\\_2 being in the 'injured' state, conditional on the all variables in the Markov blanket for injured\\_2.",
    escape = F
  ) %>%
  kable_styling(latex_options = "HOLD_position") %>%
  pack_rows("Highest", 1, 3) %>%
  pack_rows("Lowest", 4, 6) %>%
  row_spec(0,bold=TRUE)
```

@@

```{r include=FALSE, warning=FALSE}
set.seed(1003)
bmtable <- tidy(bm1, effects = "fixed") %>% 
  select(term:conf.high) %>% 
  dendroTools::round_df(2) %>% 
  mutate_at(vars(conf.low, conf.high), list(~format(round(., 2), nsmall = 2))) %>%
  mutate(conf.low = str_c("[", conf.low, sep = ""),
         conf.high = str_c(conf.high, "]", sep = "")) %>% 
  unite(., "95% CI", c("conf.low", "conf.high"), sep = ", ") %>% 
  mutate("95% CI" = str_replace_all(`95% CI`, " ", ""),
         "95% CI" = str_replace_all(`95% CI`, ",", ", ")) %>% 
  slice(1:4) %>% 
  mutate(term = c("Intercept", "RMSSD", "BIS", "RMSSD:BIS"))

@@

# Disclosure/Conflict-of-Interest Statement {-}

<!--  
Frontiers follows the recommendations by the International Committee of Medical
Journal Editors (http://www.icmje.org/ethical_4conflicts.html) which require
that all financial, commercial or other relationships that might be perceived by
the academic community as representing a potential conflict of interest must be
disclosed. If no such relationship exists, authors will be asked to declare that
the research was conducted in the absence of any commercial or financial
relationships that could be construed as a potential conflict of interest. When
disclosing the potential conflict of interest, the authors need to address the
following points:

 - Did you or your institution at any time receive payment or services from a
   third party for any aspect of the submitted work?
 - Please declare financial relationships with entities that could be perceived
   to influence, or that give the appearance of potentially influencing, what
   you wrote in the submitted work.
 - Please declare patents and copyrights, whether pending, issued, licensed
   and/or receiving royalties relevant to the work.
 - Please state other relationships or activities that readers could perceive to
   have influenced, or that give the appearance of potentially influencing, what
   you wrote in the submitted work.
 -->

@@

# Author Contributions {-}

@@

# Acknowledgments {-}

Funding:

@@

# Figures {-}

>>>>

```{r include=FALSE}
options(scipen=999, digits = 2)
knitr::opts_chunk$set(echo = FALSE)
# source("r-files/functions.R")
# source("r-files/methods_code.R")
# source("r-files/results_code.R")
load("all_data.RData")
pacman::p_load(tidyverse, knitr, kableExtra, qwraps2, brms, broom.mixed, bnlearn, tidyselect, Rgraphviz)
library(readxl)
library(janitor)
library(irr)
library(lavaan)
library(caret)
library(parallel)
library(zoo)
library(sjmisc)

\section{Introduction}

@@

\section{Methods}

@@

\subsection{Participants}

@@

BNs have recently been used in the sport psychology literature [@Olmedilla2018; @Fuster-Parra2017] and offer several benefits over traditional statistical analysis. 
For example, predictions can be made about any variable in the network, rather than there being a distinction between dependent and independent variables in the data, such as in linear regression models that are often used within the sport psychology literature [@Olmedilla2018; @Bittencourt2016].
Furthermore, the structure of a network can be obtained from both empirical data _and_ prior knowledge about the area of study; the latter being particularly useful when there are a large number of variables in the network, or only a small number of observations are available in the data [@Xiao-xuan2007].
In such instances, a purely data driven approach to learning the network would be time-consuming due to the large parameter space, and inefficient at identifying an approximation of the true network structure. 
Prior knowledge about dependencies between variables can therefore be included in the network structure, while still allowing a data driven approach for unknown dependencies, to improve the overall computation of the network structure [@Heckerman1995; @Xu2015].
The following sections detail the steps taken in the current study to firstly prepare the data for each network, and then obtain the structure of each network that was used for further inference.

### First network

#### Data Preparation

@@

A median split technique was used to discretise the data used in the network into "Low" and "High" levels.
All variables apart from negative and total life events were approximately normally distributed (based on visual inspection, see supplementary material Sx) and required no further transformation prior to the median split. 
For the LESCA questionnaire data, a cumulative total of the current, and previous time points was calculated at each time point to account for the potential continuing effect of the life events experienced by athletes over time.
Given the limited support for a relationship between positive life events and injury [@Williams2007], only negative and total life events were included in the network.
Cumulative negative, and cumulative total life event scores at each time point were first log scaled so distributions were approximately normal, and then binarised using the median at each time point (nlelg and tlelg respectively).
In addition to the log scaled cumulative values, an untransformed NLE score from the first time point was included as an additional variable based on previous literature that indicates this variable should have a strong relationship with injury outcome [@Ivarsson2017].

#### Network structure

@@

```{r table2, results='asis'}
# exampledata <- tibble(
#   Participant = c("1", "1", "2", "3", "3"),
#   "X_1" = c("T1", "T2", "T1", "T1", "T2"),
#   "link" = "->",
#   "X_2" = c("T2", "T3", "T2", "T2", "T3")
# )
# 
# kable(
#   exampledata,
#   caption = "Example of the data arrangement used for the network.",
#   escape = FALSE
# ) %>%
#   kable_styling(latex_options = "HOLD_position") %>%
#   row_spec(0, bold = TRUE)
```

#### Preliminary network structures

@@

Preliminary network structures also revealed strong dependencies between the same variables at subsequent time points. 
For example, the probability that stiffness_1 and stiffness_2 were both "High", or both "Low" was approximately 80%. 
Including the arcs between the same variables from X_1 $\rightarrow$ X_2 did not provide any theoretically meaningful information to the network structure as the majority of participants would be either be in a "Low" or "High" state for each pair of variables in the network. Therefore, these arcs were blacked listed from the network.

To obtain the final network, the appropriate blacklist and whitelists were provided and a Tabu search algorithm identified the remaining structure of the network. 
The final network structure was obtained by averaging 1000 bootstrapped models [@Efron1993] to reduce the impact of locally optimal, but globally suboptimal network learning, and to obtain a more robust model [@Olmedilla2018].
Arcs that were present in at least 30% of the models were included in the averaged model.
The strength of each arc was determined by the percentage of models that the arc was included in, independent of the arc's direction.
An arc strength of 1 indicates that the arc is always present in the network, with the value decreasing as arcs are found in fewer networks. 
In the respective study arcs above 0.5 were considered "significant" with arcs below 0.5 and above 0.3 "non-significant" [@Scutari2013]. 
Arcs below 0.3 were not included in the model.
The full table of arc strengths for the first and second network are available in S2 Table and S3 Table respectively.

#### Network Inference

@@

### Second network

#### Data preparation

For the second network, continuous variables suffixed with _1 were subtracted from variables suffixed with _2 to obtain the difference between variables measured at time points T1 $\rightarrow$ T2 and T2 $\rightarrow$ T3. 
Independent variables were then standardised (mean-centred at 0) to allow relative changes between variables to be compared. 
The "injured" variable was also modified to represent whether a participant had sustained an injury at any point over the duration of the study or were healthy for the duration of the study.
Setting the data up in this way enabled the construction of a network that explicitly modelled the _amount_ of change within variables between time points, as opposed to the first network that would only have captured changes when the median threshold was crossed from "Low" to "High".

#### Network structure

Similar to the first network, blacklists were used to prevent arcs from independent variables $\rightarrow$ explanatory variables.
In addition, "nlebase" variable was dropped from the list of explanatory variables to allow the _changes_ in negative life events to be the only life event variable in the network. 
The final network was obtained using the same approach as the first network.

#### Network Inference

Conditional probability queries (CPQ) were again used to perform inference the network structures.
The Markov blanket of the "injured" node was of particular interest, and the probability of injury was investigated with combinations of variables in the Markov blanket below the mean change, at the mean change and above the mean change.
Initial visual inspection of the network structure also revealed arcs between BIS $\rightarrow$ FFFS and HRV $\rightarrow$ FFFS. 
To investigate this relationship further, random samples were generated for BIS, HRV and FFFS based on the conditional distribution of the nodes included as evidence in the query.
The samples were then examined using a Bayesian linear regression models with the _brms_ package [@Burkner2017a] to determine the relationship between these nodes. 
Weakly regularising priors (normal prior with mean of 0 and standard deviation of 5) were used for all parameters in the model.

@@

## First network structure

@@

<!-- The conditional probabilities based on all the variables in injured_2 Markov blanket are presented in Table \ref{tab:table9}. -->
<!-- Again, only the three lowest and highest probabilities are shown (complete results in S5 Table). -->
<!-- The combination "Low" FFFS_1, "High" stiffness_2, "High" balance resulted in the greatest  probability of injured_2 being "injured", with the highest probability of injury being `r max(query4$prob)`. -->
<!-- With all other variables held in the "High" state, the probability of injured_2 being "injured" rose from 0.14 to 0.34 when FFFS_1 was in the "Low" compared to "High" state. -->
<!-- The combination of "Low" stiffness, "Low" balance and "High" FFFS resulted in the lowest probability of injured_2 being "injured". -->

<!-- ```{r table9, results="asis" } -->

<!-- query4 %>% -->
<!--   select(7,2:6) %>% -->
<!--   rename(Probability = "prob") %>% -->
<!--   `colnames<-`(str_replace_all(colnames(.), "_", "\\\\_")) %>% -->
<!--   mutate_all(~str_replace_all(., "_", "\\\\_"))%>% -->
<!--   kable( -->
<!--     ., -->
<!--     caption = "Highest and lowest probability of injured\\_2 being in the 'injured' state, conditional on the all variables in the Markov blanket for injured\\_2.", -->
<!--     escape = F -->
<!--   ) %>% -->
<!--   kable_styling(latex_options = "HOLD_position") %>% -->
<!--   pack_rows("Highest", 1, 3) %>% -->
<!--   pack_rows("Lowest", 4, 6) %>% -->
<!--   row_spec(0,bold=TRUE) -->
<!-- ``` -->

@@

```{r include=FALSE, warning=FALSE}
set.seed(1003)
bmtable <- fixef(bm1) %>% 
  as_tibble(rownames = "term") %>% 
  `colnames<-`(c("Term", "Estimate", "Error", "conf.low", "conf.high")) %>% 
  dendroTools::round_df(2) %>%
  mutate_at(vars(conf.low, conf.high), list(~format(round(., 2), nsmall = 2))) %>%
  mutate(conf.low = str_c("[", conf.low, sep = ""),
         conf.high = str_c(conf.high, "]", sep = "")) %>%
  unite(., "95% CI", c("conf.low", "conf.high"), sep = ", ") %>%
  mutate("95% CI" = str_replace_all(`95% CI`, " ", ""),
         "95% CI" = str_replace_all(`95% CI`, ",", ", "))

@@

Informed by Appaneal and Perna’s (2014) extension to the widely cited Williams and Anderson's (1998) stress-injury model, the purpose of this study was to examine how psychosocial stress-related factors, and physiological stress-related markers may interact and act synergistically to increase the risk of injury; therein addressing several of the limitations of the sport injury literature [@Johnson2014].
Potential relationships between psychosocial stress-related factors, physiological stress-related markers of stress and injury were investigated using two BN structures; the first was a two-time Bayesian Network that investigated the relationships between variables _across_ time points in the study (Fig \ref{fig:fig5}), and the second network used differential equations to model the changes in variables _between_ time points (Fig \ref{fig:fig8}).

The first network revealed several links between the injured nodes and other variables in the network.
For example, Fig \ref{fig:fig6} and Fig \ref{fig:fig7} show the Markov blankets for the injured_1 and injured_2 nodes in the first network and include all the variables that had a direct effect on the probability of injury.
The combination of high stiffness and poor balance resulted in the highest probability of injury in the Markov blankets for injured_1 and injured_2.
The presence of these factors at both injured nodes indicates that the combined action of these variables is important for determining an athlete's risk of injury. 
In the second network, the highest probability of injury was observed when changes in stiffness _and_ negative life events were both greater than average (Table \ref{tab:table11}), indicating that the combination of changes in psychological and physiological measures of stress may combine additively to increase the risk of injury [@Appaneal2014].
Table \ref{tab:table7} shows the combinations of variables that resulted in the highest and lowest probabilities of injury conditional on all explanatory variables and variables suffixed with _1.
Although only the highest and lowest values are shown, there were over 16000 possible combinations of variables states that could influence the risk of injury.
The adopted approach attempts to take the complex systems view of injury recommended by Bittencourt et al. [@Bittencourt2016], where injury is an emergent property from a web of determinants that interact in different ways.

Of all the variables measured in the study, muscle stiffness appeared to be most strongly related to injury.
Both "High" levels of stiffness in the first network, and greater than average increases in stiffness in the second network were found to increase the risk of injury.
In this study, a novel hand-held device (MyotonPRO) was used to measure muscle stiffness.
To date, one of only a small number of studies that have used the MyotonPRO to explore the relationship between muscle stiffness and sports injury, found that increased muscle stiffness in the soleus and Achilles tendon was related to increased injury incidence in elite level netball players [@PickeringRodriguez2017].
The results of the current study build on these findings, with a larger sample of athletes from a range of different sports, strengthening the evidence for a relationship between higher levels of muscle stiffness and injury.
However, high levels of muscle stiffness, as measured by the MyotonPRO, have also been found to be related to improved performance, with elite level athletes having increased lower extremity stiffness [@Pruyn2015; @Kalkhoven2018].
Collectively, therefore, these findings suggest that while muscle stiffness plays a vital role in performance, increased levels of stiffness also increase the risk of injury, with each athlete likely to have an optimum level of stiffness that maximises performance while minimising the risk of injury [@Butler2003].
Additionally, high stiffness may only increase the risk of injury if other factors are also present.
To elaborate, the combination of high stiffness _and_ poor balance was found to result in the greatest probability of injury.
In contrast, athletes with high stiffness and good balance were less likely to be injured, suggesting that improved postural stability may counteract the potential harmful effects of high levels of muscle stiffness.
Several studies have identified how balance [@Romero-Franco2014; @Trojian2006] and muscle stiffness [@Butler2003; @PickeringRodriguez2017] are related to injury individually; however this study has demonstrated how these two factors may have an additive effect in relation to injury occurrence.

In addition to stiffness, balance is also linked to injury at both injured nodes in the first network, however the strength of the arc was only 0.35 and 0.30 from balance $\rightarrow$ injured_1 and balance $\rightarrow$  injured_2 respectively.
Despite the weak arc strength, a "High" balance score, indicating impaired postural stability, was found to increase the probability of injury.
This finding is consistent with previous research that has reported an association between decrements in postural stability and increased injury risk [@Riemann1999d; @Romero-Franco2014; @Trojian2006].
Postural stability is often used as an indicator of athlete performance level, with higher level athletes demonstrating better postural stability over their lower level counterparts [@Paillard2006].
In the current study, athletes who competed at a higher level were also more likely to have good balance ("Low" balance), compared to their lower level counterparts.
These findings suggest that better postural stability is associated with both a higher level of performance and a lower probability of sustaining an injury, reinforcing the importance of postural stability as a feature of athletic training programmes designed to prepare athletes for the demands of high intensity training and competition [@Hrysomallis2011].

Of the psychological variables in the study, negative life events have previously been reported to be most strongly associated with injury [@Williams2007; @Ivarsson2017].
In the current study, the second network revealed that greater than average increases in negative life event stress increased the probability of being injured during the study period.
However, negative life event stress had almost no effect on the probability of injury in the first network.
This finding suggests that the _relative change_ in life events may be more important than the _absolute score_ for life events, despite the latter being commonly used in sports injury research to date.
For example, an athlete who reports a negative life event score of 1 during the first time point, but then a score of 5 at the second time point will have a 400% increase in their life event score.
Although the absolute score would be "Low", the relative increase could have been caused by a significant event in the athlete's life, that could have a considerable psychological and physiological effect [@Appaneal2014].
Future research should therefore consider study designs and appropriate analysis methods that enable relative changes in an individual athlete's life events to be assessed [cf. @Ivarsson2014].

The finding that negative life events had almost no impact on the probability of injury in the first network was surprising given that the majority of research has consistently identified major life events, particularly those events with a _negative_ valence, as the strongest predictor of injury in Williams and Andersen's [@Williams1998] model [@Ivarsson2017].
During the initial network structure development, no arcs between the negative life event nodes and injured nodes were found by the Tabu search algorithm.
However, given the strength of the literature indicating that negative life events are related to injury, an arc was fixed between nlelg_1 $\rightarrow$ injured_1 and nlelg_2 $\rightarrow$ injured_2 to allow this relationship to be examined more closely.
When negative life events were "High" the probability of injury showed a negligible change at the injured_1 node and decreased by `r query3[3,3] - query3[3,2]` at the injured_2 node.
One possible explanation for these findings may be due to the use of the LESCA questionnaire in a repeated measures design.
In the original LESCA instructions, participants are asked to report major life events that have occurred over the previous 12-months [@Petrie1992].
However, in the current study, participants completed the LESCA at approximately 4-month intervals after baseline and were therefore asked to report any events which had occurred _since the previous data collection session_, to avoid inflated scores caused by reporting the same event on multiple occasions.
The reduced 4-month time interval between data collections may have reduced the likelihood for life events listed in the LESCA to have taken place.
For example, at the second and third time points, 26% of participants reported 0 negative life events for the preceding four-month period.
Simply, it may be that the items on the LESCA are less suitable for repeated measurements with durations shorter than the original 12-months than a measure that captures minor life events [cf. @Fawkner1999].

Another possible explanation for the findings for major/negative life events is that participants in the study may have had access to the necessary coping resources to mitigate against the effects of any negative life event stress they experienced.
Williams and Andersen's [@Williams1998] model proposed a number of coping resources that were either directly related to injury or moderated the relationship between life stress and injury occurrence; for example, general coping strategies (e.g., good sleeping habits and self-care), social support systems and stress management skills.
Although coping was not measured in the current study, several studies have found high levels of social support can reduce the risk of injury [@Petrie1993; @Petrie2014; @Johnson2014].
Therefore, future research should consider including a measure of coping alongside that of life event stress to help explain the possible moderating effect.

Of the remaining variables, both FFFS and RMSSD were also linked to injury.
A weak arc was observed between RMSSD_2 $\rightarrow$ injured_2 (arc strength = 0.30), however no arc was present between RMSSD_1 and injured_1, suggesting the link between RMSSD and injury was weaker than muscle stiffness and balance, where stronger arcs existed at both of the injured nodes.
Despite the uncertainty regarding the relationship between injury and RMSSD in the first network, "Low" RMSSD increased the probability of injury from 0.17 (RMSSD = "High'') to 0.27 (RMSSD = "Low'').
This finding is consistent with previous research that has found reduced RMSSD to be indicative of illness or maladaptation to training due to decreased parasymapthic activity, which often precedes injury [@Williams2017; @Bellenger2016; @Gisselman2016].
An arc between FFFS_1 and injured_2 (arc strength = 0.40) was also observed in the first network, where the risk of injury was increased from 0.13 to 0.29 with FFFS in the "High" and "Low" states respectively.
Interestingly, the "Low" FFFS score was also related to injuries at subsequent time points; for example, the "Low" FFFS recorded at the first time point was related to injuries recorded at the second time point in the study.
One possible explanation for this finding could be that those athletes who reported "Low" FFFS score were less fearful, and may therefore engage in more risk taking behaviours, increasing the probability of injury.
The RST theory proposes that higher levels of FFFS increase avoidance motivation [@Corr2016b], and therefore "High" FFFS may have acted as a deterrent from taking risks while training and competing, reducing exposure to situations that could have resulted in injury.

In the first network, "High" BIS was associated with "High" FFFS, while in the second network, increases in BIS were associated with increases in FFFS.
RST proposes that the combination of high BIS and high FFFS is likely to result in a more anxious disposition due to high levels of avoidance and high goal conflict characterised by high levels of FFFS and BIS [@Corr2013].
High levels of anxiety and anticipation of stressful situations have been associated with reductions in HRV indices including RMSSD [@Chalmers2014; @Pulopulos2018], which is supported by the negative relationship between FFFS and RMSSD in the second network (Table \ref{tab:table10}). 
These findings align with the proposed actions of the RST theory [@Corr2016b]. 
For example, high levels of BIS are proposed to be the result of goal conflict between the FFFS (avoidance) and BAS (approach) systems. 
The goal conflict is likely to elicit a physiological response (e.g., decreased HRV) in preparation to engage in the required behaviour to resolve the goal conflict [@Corr2016b].
To extend these findings, the BAS should also be considered. 
Specifically, to establish how the BAS and FFFS interact, and how these two systems affect the BIS.
However, in the current study, initial network structures revealed the BAS sub-scales to have limited connectivity with other measures in the network, therefore only one of the BAS sub-scales (RI) was included in the final network structure.
In the first network, RI_1 was connected to both BIS_1 and BIS_2, and in both instances, the probability of "High" BIS was increased when RI was also "High". 
However, the arcs between RI_1 and BIS were weak (< 0.50), and RI represents only one component of the BAS system. 
Other BAS factors such as impulsivity may be more closely related to risk-taking behaviours and may reveal additional links to sports injury. 
Therefore, a more detailed examination of the different elements of RST, and specifically the BAS in relation to injury occurrence is warranted.

The current research had several strengths, including the longitudinal repeated measures design and modelling approach.
A major critique of the sport injury literature has been the use of only one wave of measurement that may not be reflective of and capture the dynamic nature of the variables that are associated with injury [@Johnson2014].
The longitudinal repeated measures design of the current study allowed _changes_ over time and between time points to be captured and explored.
Another significant strength of the current research was the interdisciplinary approach, which enabled an examination of the complex interplay between psychosocial and physiological markers of stress.
Although there are unique and significant challenges with research employing longitudinal repeated measures designs, they provide for far more fine-grained understanding of the dynamic relationships between stress-related factors and injury occurrence in athletes.
Sport injury research has been criticised for adopting analytic approaches that are reductionist in nature [@Bittencourt2016] that fail to account for the complex, emergent behaviour that is characteristic of injury occurrence.
To address this issue, Bayesian networks (BN) were used to more closely align with the complex, multifactorial nature of injury.
The networks allowed several markers of stress that were free to interact with each other, as well as injury, to be explored.
Consequently, BN's provided a contemporary approach that improved upon traditional methods such as logistic regression [@Olmedilla2018].

As with most research, there were several limitations with the present study.
Firstly, the choice was made to binarise variables in the first network so only "Low" and "High" states were observed.
Although binarising variables is a common procedure in Bayesian network analysis and has several advantages, Qian and Miltner @Qian2015 highlighted that both a loss of statistical accuracy and potential difficulty in subsequent interpretation of the model may arise when following a binarising procedure.
For example, the meaning of a "Low" and "High" value in the current study is only meaningful for the population that was studied, and there could be additional levels within each category that were not investigated.
A second limitation was the nature of the physiological measures used in the current study.
In order to collect data on a large sample of participants, suitable measures were required to ensure the viability of the data collection; however, some of these measures may not have been sensitive enough to detect more subtle variation in athletes.
For example, postural stability could have been assessed with the use of a force plate, which is considered the gold standard, to provide detailed data and enable a more fine-grained analysis [@Ross2011].

In addition to the future directions already outlined, the findings from the current study offer several avenues for future research.
Although the current study used a range of measures to capture "stress" from both a psychological and physiological perspective, there may be additional measures available that could provide further insight into the relationship between stress-related factors and sports injury.
For example, stress hormones such as cortisol have been found to be a marker of both psychological and training-related stress [@Appaneal2014; @Perna1995], and could help elucidate the relationship between stress and injury.
Additionally, although the LESCA is the most widely used measures of major life events in sports injury research, the current study found several limitations with using the LESCA in a repeated measures design, including how the items were scored.
For example, there is no way to differentiate between an athlete who has answered four items as moderately negative, and one item as extremely negative.
Both responses would be scored a "-4"; however, there could be vastly different psychological and physiological effects between moderately negative and extremely negative events. Therefore, future research could develop a modified version of the LESCA that could distinguish between these types of responses and their effects.

In conclusion, the purpose of this research was to explore the multifaceted nature of the stress-injury relationship, and several psychosocial and physiological markers were found to combine and exacerbate the risk of injury.
Specifically, muscle stiffness and _increases_ in negative life event stress were identified as strong predictors of injury, while other factors including personality characteristics and postural stability were also found to contribute to the probability of injury occurrence.
Taken together, the interdisciplinary approach coupled with the advanced analytical techniques used and complex systems framework has provided a novel examination of the stress-injury relationship that has addressed many of the limitations identified in previous research.

# Disclosure/Conflict-of-Interest Statement

@@

# Author Contributions

@@

@@

# Figures
